\documentclass[a4paper,10.5pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[top=0.5in, bottom=0.5in, left=0.6in, right=0.6in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}

% Remove page number
\pagestyle{empty}

% Section formatting - matching reference CV
\titleformat{\section}
  {\normalsize\bfseries\uppercase}
  {}
  {0em}
  {}
  [\titlerule]

\titlespacing*{\section}{0pt}{8pt}{4pt}

% Hyperlink setup - underlined black links
\hypersetup{
  colorlinks=true,
  urlcolor=black,
  linkcolor=black,
  pdfborder={0 0 0}
}
\urlstyle{same}

% Remove paragraph indent
\setlength{\parindent}{0pt}

% Custom commands
\newcommand{\entrytitle}[2]{%
  \textbf{#1} \hfill #2%
}

\newcommand{\entrysubtitle}[2]{%
  \textit{#1} \hfill \textit{#2}%
}

\begin{document}

% ===================== HEADER =====================
\begin{center}
  {\Large\textbf{MUHAMMAD AHMAD}} \\[3pt]
  Lahore, Pakistan \enspace$|$\enspace +92 337 1479647 \enspace$|$\enspace \href{mailto:muhammadahmad171105@gmail.com}{muhammadahmad171105@gmail.com} \\
  \href{https://linkedin.com/in/muhammad-ahmad17}{linkedin.com/in/muhammad-ahmad17} \enspace$|$\enspace \href{https://github.com/muhammad-ahmad17}{github.com/muhammad-ahmad17} \\[3pt]
  \textbf{Computer Engineering Student $|$ Focus: Backend Development \& DevOps}
\end{center}

% ===================== OBJECTIVE =====================
\section{Objective}
6th semester Computer Engineering student at COMSATS University with a passion for backend development and DevOps. Experienced in building REST APIs with Node.js and Express, working with SQL and NoSQL databases, and exploring cloud services on AWS. Seeking internship opportunities to contribute to real-world engineering teams.

% ===================== EXPERIENCE =====================
\section{Experience}

\entrytitle{Innovative Saudia}{Jul 2025 -- Aug 2025} \\
\entrysubtitle{Backend Engineer Intern}{Lahore} \\
\small\textit{\href{https://github.com/Muhammad-Ahmad17/Internship}{Daily Progress Log \& Work}}
\normalsize
\begin{itemize}[nosep, leftmargin=1.5em, topsep=2pt]
  \item Learned backend and DevOps practices under the guidance of experienced professionals.
  \item Documented daily progress and key learnings to track skill growth.
  \item Prepared for the AWS Cloud Practitioner certification, completing multiple mock tests.
\end{itemize}

\vspace{4pt}

\entrytitle{Self-Employed}{2024 -- Present} \\
\entrysubtitle{Freelance Web Developer}{Lahore}
\begin{itemize}[nosep, leftmargin=1.5em, topsep=2pt]
  \item Completed 1+ freelance projects for local clients, handling deployment and hosting.
  \item Gained practical experience in client communication and project management.
\end{itemize}

% ===================== EDUCATION =====================
\section{Education}

\entrytitle{COMSATS University Islamabad, Lahore Campus}{2023 -- 2027} \\
\textit{Bachelor of Computer Engineering} \hfill \textit{Lahore} \\
\textit{CGPA: 3.6/4.0 $|$ 6th Semester}

% ===================== PROJECTS =====================
\section{Projects}

\textbf{Multi-Buyer \& Vendor E-Commerce Platform} \hfill
\small\href{https://github.com/Muhammad-Ahmad17/E_Commerce}{GitHub}
\enspace$|$\enspace
\href{https://e-commerce1-muhammad-ahmads-projects-1458b467.vercel.app/}{Live Demo}
\normalsize
\begin{itemize}[nosep, leftmargin=1.5em, topsep=2pt]
  \item Built a full-stack e-commerce app with multi-role support (Buyer, Vendor) using 3-tier architecture.
  \item Implemented authentication, order management, and REST APIs with Node.js and Express.js.
  \item \textbf{Tech stack:} React, Node.js, Express.js, SQL Server.
\end{itemize}

\vspace{4pt}

\textbf{Serverless User Processing System} \hfill
\small\href{https://github.com/Muhammad-Ahmad17/getApiForUserData}{GitHub}
\enspace$|$\enspace
\href{http://user-processing-system-ahmad.s3-website-us-east-1.amazonaws.com/}{Live Demo}
\normalsize
\begin{itemize}[nosep, leftmargin=1.5em, topsep=2pt]
  \item Developed a React frontend with a serverless backend using AWS Lambda triggered by API Gateway.
  \item Integrated DynamoDB for data storage and hosted on S3 as a static website.
  \item \textbf{Tech stack:} React, AWS Lambda, API Gateway, DynamoDB, S3.
\end{itemize}

\vspace{4pt}

\textbf{Real-Time Smart Room Automation System} \hfill
\small\href{https://github.com/Muhammad-Ahmad17/RealTimeSmartRoomAutomation}{GitHub}
\normalsize
\begin{itemize}[nosep, leftmargin=1.5em, topsep=2pt]
  \item Built an embedded system using STM32F407 with RFID access, motion detection, and temperature monitoring.
  \item Implemented multi-sensor data fusion with real-time LCD feedback and buzzer alerts.
  \item \textbf{Tech stack:} STM32F407, C/Embedded C, HAL Library, I2C, SPI, ADC, DMA.
\end{itemize}

% ===================== TECHNICAL SKILLS =====================
\section{Technical Skills}

\begin{itemize}[nosep, leftmargin=1.5em, topsep=2pt]
  \item \textbf{Languages:} JavaScript, Python, C, C++, SQL, VHDL.
  \item \textbf{Backend:} Node.js, Express.js, REST APIs, MongoDB, SQL Server.
  \item \textbf{Frontend:} React, Next.js, Tailwind CSS, HTML/CSS, Framer Motion.
  \item \textbf{Cloud \& DevOps:} AWS (Lambda, S3, DynamoDB, API Gateway), Docker, GitHub Actions, Vercel, Linux, Git.
  \item \textbf{Hardware:} STM32, Microcontrollers, FPGA (VHDL), Embedded Systems.
  \item \textbf{Tools:} VS Code, Postman, MongoDB Compass, Figma, Chrome DevTools.
\end{itemize}

\end{document}
